Probabilistic Programming

### 2014-04-21 paper/paper.tex
Small paper edits

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}   
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{float}
\usepackage{hyperref}
\usepackage{listings}
\usepackage[margin=3.75cm]{geometry}

@@

In the current implementation of this system, following the paths [\emph{Identifier}, \emph{Name}], or [\emph{Literal}, \emph{Raw}] result not in node types, but rather in the text of the identifier names or literal values. This way, generating identifiers and literals is simply a probabilistic process like the rest of the code generation. Of course, this means that sometimes identifiers are added that are not in scope, that have mismatched types, or that simply make no semantic sense. (But adjusting $depth$ did seem to make programs more meaningful, as expected. This can be seen experimentally by modifying depth on our web IDE, which explained in Section 4.1.)

@@

We integrated our model into the text editor vim to offer autocompletion
suggestions of programs upon the user's request, using vim's
\texttt{completefunc} feature. When the user is editing a JS file in vim with
this feature, they may press a keyboard command to get a list of program
snippets to choose from. The snippets are generated in the context of the
program path at cursor's position. The user may pick one of the snippet
suggestions to have it inserted into their code at their cursor.

The autocomplete snippets are generated as follows:
\begin{enumerate}
	\item Parse the contents of the current file into an AST.
	\item Find the node path corresponding to the cursor by traversing the AST.
	\item Generate programs starting from the node path of the cursor.
	\item Present the programs to the user as code completion snippets.
\end{enumerate}

\begin{figure}[ht]
	\centering
	\begin{tabular}{c c}
		\begin{subfigure}[h]{6.25cm}
			\centering
			\includegraphics[width=1.00\textwidth]{vim1}
			\caption{Inserting a for loop} \label{fig:vim1}
		\end{subfigure}
		\begin{subfigure}[h]{6cm}
			\centering
			\includegraphics[width=1.00\textwidth]{vim2}
			\caption{Inserting an object property} \label{fig:vim2}
		\end{subfigure}
	\end{tabular}
	\caption{Screenshots of vim using autocomplete of programs}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=1.00\textwidth]{ide}
  \caption{Screenshot of the web program editor GUI} \label{fig:screenshot}
\end{figure}

@@

We explored several other approaches that could solve the issue of identifiers and literals.

@@

\subsubsection{Secondary models for identifiers}

@@

We suspect that this may affect the complexity of our algorithms significantly. If what the system is doing now is analogous to the behavior of a context-free grammar (i.e. by recursively generating nodes), having detection of bound (same) identifiers across nodes would involve pattern-matching and, perhaps even analogy-solving, could be considered more of an action of a Turing machine. This could mean the complexity of the process could be unbounded.

@@

\subsubsection{Extending the model}

@@

\section{Conclusions}

@@

\subsection*{Source \& Demo}

@@

\begin{figure}[h!]
	\caption{ast-sample.json}
	\label{fig:sample-ast}
	\centering
	An AST generated from the program ``var x = 34;"

@@

\begin{figure}[h!]
	\caption{model-sample.json}
	\label{fig:sample-model}
	\centering
	A model generated from the program ``var x = 34;"

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}   
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{float}
\usepackage{hyperref}
\usepackage{listings}
\usepackage[labelfont=bf]{caption}
\usepackage[margin=3.75cm]{geometry}

@@

In the current implementation of this system, following the paths [\emph{Identifier}, \emph{Name}], or [\emph{Literal}, \emph{Raw}] result not in node types, but rather in the text of the identifier names or literal values. This way, generating identifiers and literals is simply a probabilistic process like the rest of the code generation. Of course, this means that sometimes identifiers are added that are not in scope, that have mismatched types, or that simply make no semantic sense. (But adjusting $depth$ did seem to make programs more meaningful, as expected. This can be seen experimentally by modifying depth on our web IDE, which is discussed in Section 4.1.)

@@

We integrated our model into the text editor vim to offer autocompletion
suggestions of programs upon the user's request, using vim's
\texttt{completefunc} feature. When the user is editing a JavaScript file in vim with
this feature, they may press a keyboard command to get a list of program
snippets to choose from. The snippets are generated in the context of the
program path at cursor's position. The user may pick one of the snippet
suggestions to have it inserted into their code at their cursor. The autocomplete snippets are generated as follows:
\begin{enumerate}
	\item Parse the contents of the current file into an AST.
	\item Find the node path corresponding to the cursor by traversing the AST.
	\item Generate programs starting from the node path of the cursor.
	\item Present the programs to the user as code completion snippets.
\end{enumerate}

\begin{figure}[ht]
	\centering
	\begin{tabular}{c c}
		\begin{subfigure}[h]{6.25cm}
			\centering
			\includegraphics[width=1.00\textwidth]{vim1}
			\caption{Inserting a {\tt for} loop} \label{fig:vim1}
		\end{subfigure}
		\begin{subfigure}[h]{6cm}
			\centering
			\includegraphics[width=1.00\textwidth]{vim2}
			\caption{Inserting an object property} \label{fig:vim2}
		\end{subfigure}
	\end{tabular}
	\caption{Screenshots of vim using autocomplete of programs}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=1.00\textwidth]{ide}
  \caption{Screenshot of the web program editor GUI. The header along the top indicates the path (trimmed to the selected depth) to the current position of the cursor. Code snippets on the left can be navigated using the arrow keys.} \label{fig:screenshot}
\end{figure}

@@

@@

\subsection{Intelligent handling of identifiers and literals}

We explored other approaches to solve the issue of generating meaningful identifiers and literals described before.

\subsubsection{Secondary models}

@@

We suspect that this may affect the complexity of our algorithms significantly. If what the system is doing now is analogous to the behavior of a context-free grammar (i.e. by recursively generating nodes), then detection of use of the same identifiers across nodes would involve pattern-matching and perhaps even analogy-solving. This could analogously be considered more like the action of a Turing machine, which would mean that the complexity of the process could be unbounded.

@@

\subsubsection{Using a higher-order model}

@@

\section{Conclusion}

@@

\subsection*{Source code \& demo}

@@

\begin{figure}[h!]
	\caption{JSON AST sample}
	\label{fig:sample-ast}
	\centering
    \vspace{-7pt}
	An AST generated from the program ``{\tt var x = 34;}"

@@

\begin{figure}[h!]
	\caption{JSON Markov model sample}
	\label{fig:sample-model}
	\centering
    \vspace{-7pt}
	A Markov chain model generated from the program ``{\tt var x = 34;}"
